---
title: "Homework-10.23"
author: "丁婧琦"
date: "2023-10-23"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to R-package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##  Question
Refer to Exercise 7.4. Compute 95% bootstrap confidence intervals for the mean time between failures 1/λ by the standard normal, basic, percentile,and BCa methods. Compare the intervals and explain why they may differ.

## Answer
\
首先，采用boot函数来生成置信区间。然后对比这四种置信区间的结果。
```{r}
library(boot)
set.seed(1234)
aircondit <- as.matrix(aircondit)
BOOT.mean <- function(x,j) mean(x[j])
BOOT.obj <- boot(aircondit, statistic=BOOT.mean, R=2000)
print(boot.ci(BOOT.obj, type = c("norm","basic","perc","bca")))
```
由结果可知,"normal,basic,percentile,BCa"四种类型的置信区间结果都不一样。四类置信区间的公式如下：
\
1.normal(The standard bootstrap CI based on asymptotic normality):$$\left (  \hat{\theta} -z_{1-\alpha }\hat{se} ,\hat{\theta} -z_{\alpha }\hat{se} \right ) $$

2.basic(The basic bootstrap CI based on the large sample property):$$\left (  2\hat{\theta} -\hat{\theta}_{1-\alpha/2}^* ,2\hat{\theta} -\hat{\theta}_{\alpha/2}^* \right )$$

3.percentile(Percentile CI (percent) by assuming $\hatθ^*|X , \hatθ$ have approximately the same distribution):$$\left (  \hat{\theta}_{\alpha/2}^* ,\hat{\theta}_{1-\alpha/2}^* \right )$$


4.BCa(Bias-corrected and accelerated CI):$$\left (  \hat{\theta}_{\alpha_1}^* ,\hat{\theta}_{\alpha_2}^* \right )$$
\
由四种置信区间的计算公式的表达式可知，四种置信区的计算方法不相同，因而置信区间的结果会各有差别。

##  Question
Refer to Exercise 7.7. Obtain the jackknife estimates of bias and standarderror of $\hat\theta$.

## Answer
the jackknife estimates of bias and standarderror的计算公式如下：

$$\hat{bais}_{jack}=(n-1)(\overline{\hat\theta_{(.)}}-\hat\theta) $$
$$ \hat{se}_{jack}=\sqrt{\frac{n-1}{n}\sum_{i=1}^{n}(\hat\theta_{(i)}-\overline{\hat\theta_{(.)}}) ^2}$$
```{r}
library(bootstrap)
set.seed(1234)
#计算theta的估计值
datacov<-cov(scor)
Lambdahat<-eigen(datacov)$values
Thetahat<-Lambdahat[1]/sum(Lambdahat)
#利用刀切法
n<-nrow(scor)
Thetajack <- numeric(n)
for(i in 1:n){
  datanew<-cov(scor[-i,])
  Lambdanew<-eigen(datanew)$values
  Thetajack[i]<-Lambdanew[1]/sum(Lambdanew)
}

bias.jack <- (n-1)*(mean(Thetajack)-Thetahat)
se.jack <- sqrt((n-1)*mean((Thetajack-Thetahat)^2))
round(c(original=Thetahat,bias.jack=bias.jack,se.jack=se.jack),4)
```

##  Question
In Example 7.18, leave-one-out (n-fold) cross validation was used to select the best fitting model. Use leave-two-out cross validation to compare the models.

## Answer
采用leave-two-out cross validation和采用leave-one-out cross validation的方法较为类似，采用leave-two-out cross validation的代码如下：
```{r}
library(DAAG)
attach(ironslag)
k <- length(magnetic)
res1 <- res2 <- res3 <- res4 <- numeric(k*(k-1)/2)
# for n-fold cross validation
# fit models on leave-two-out samples
a <- 0
for (i in 1:(k-1))
  for (j in (i+1):k) {
    a <- a+1
    y <- magnetic[-c(i,j)]
    x <- chemical[-c(i,j)]
    
    Q1 <- lm(y~x)
    y11 <- Q1$coef[1]+chemical[i]*Q1$coef[2]  
    y12 <- Q1$coef[1]+chemical[j]*Q1$coef[2] 
    res1[a] <- (magnetic[i]-y11)^2+(magnetic[j]-y12)^2
    
    Q2 <- lm(y~x+I(x^2))
    y21 <- Q2$coef[1] + Q2$coef[2] * chemical[i] + Q2$coef[3] * chemical[i]^2
    y22 <- Q2$coef[1] + Q2$coef[2] * chemical[j] + Q2$coef[3] * chemical[j]^2
    res2[a] <- (magnetic[i]-y21)^2+(magnetic[j]-y22)^2
    
    Q3 <- lm(log(y)~x)
    logy31 <- exp(Q3$coef[1] + Q3$coef[2] * chemical[i])
    logy32 <- exp(Q3$coef[1] + Q3$coef[2] * chemical[j])
    res3[a] <- (magnetic[i]-logy31)^2+(magnetic[j]-logy32)^2
    
    Q4 <- lm(log(y)~log(x))
    logy41 <- exp(Q4$coef[1] + Q4$coef[2] * log(chemical[i]))
    logy42 <- exp(Q4$coef[1] + Q4$coef[2] * log(chemical[j]))
    res4[a] <- (magnetic[i]-logy41)^2+(magnetic[j]-logy42)^2
  }

res = c(mean(res1)/2,mean(res2)/2,mean(res3)/2,mean(res4)/2)
res
#table<-cbind(prediction error,Quadratic,Exponential,Log-Log)
#knitr::kable(table,align="c")
matrix(res, nrow=1, dimnames=list("prediction error", c("Linear","Quadratic"," Exponential","Log-Log")))

```
