---
title: "Homework-2023.10.16"
author: "丁婧琦"
date: "2023-10-16"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to R-package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question
考虑m=1000个假设，其中前95%个原假设成立，后5%个对立假设成立。在原假设下，P值服从U(0,1)分布。在对立假设下P值服从Beta(0.1,1)分布（可用rbeta生成）应用Bonferroni校正与B-H校正应用于生成m个P值（独立）（应用p.adjust），得到校正后的P值，与$\alpha=0.1$比较确定是否拒绝原假设。基于M=1000次模拟，可估计FWER,FDR,TPR，并输出到表格当中。

## Answer
多重假设检验对应的各项指标如下：
Given true condition:
\
False positive rate $(\mathrm{FPR})=V / m_0$
\
True positive rate $(\mathrm{TPR})=S /(m-m 0)$
\
False negative rate $($ FNR $)=T /(m-m 0)$
\
True negative rate $(T N R)=U / m_0$

Given prediction condition:
\
False discovery rate $(\mathrm{FDR})=V / R$
\
True discovery rate $(\mathrm{TDR})=S / R$
\
由于生成的m个P值独立，则FWER的计算公式如下：
$$FWER=P(V>=1)=1-P(V==0)$$它代表这犯第一类错误的概率。
```{r}
M <- 1000
p1<-runif(950)
p2<-rbeta(50,0.1,1)
p3<-c(p1,p2)
p<-sort(p3)
p.adjust1<-p.adjust(p,method="bonferroni",n=length(p))
p.adjust2<-p.adjust(p,method="fdr",n=length(p))
#计算bonferroni检验的FWER,FDR(V/R),TPR(S/M-M0)
R1=0
m0=0
v1=0
for(i in 1:length(p)){
  if(p.adjust1[i]<0.1)
    R1 <- R1+1
  if(p[i]<0.1)
    m0 <- m0+1
  if(p.adjust1[i]<0.1&&p[i]<0.1)
    v1 <- v1+1
}
S1=R1-v1
FWER1=v1/M
FDR1=v1/R1
TPR1=S1/(M-m0)
#计算BH检验的FWER,FDR(V/R),TPR(S/M-M0)
R2=0
m02=0
v2=0
for(i in 1:length(p)){
  if(p.adjust2[i]<0.1)
    R2 <- R2+1
  if(p[i]<0.1)
    m02 <- m02+1
  if(p.adjust2[i]<0.1&&p[i]<0.1)
    v2 <- v2+1
}
S2=R2-v2
FWER2=v2/M
FDR2=v2/R2
TPR2=S2/(M-m02)
```

## Question
Suppose the population has the exponential distribution with rate $\lambda$, then the MLE of $\lambda$ is $\hat{\lambda}=1 / \bar{X}$, where $\bar{X}$ is the sample mean. It can be derived that the expectation of $\hat{\lambda}$ is $\lambda n /(n-1)$, so that the estimation bias is $\lambda /(n-1)$. The standard error $\hat{\lambda}$ is $\lambda n /[(n-1) \sqrt{n-2}]$. Conduct a simulation study to verify the performance of the bootstrap method.
\
The true value of $\lambda=2$. 
\
The sample size $n=5,10,20$.
\
The number of bootstrap replicates $B=1000$.
\
The simulations are repeated for $m=1000$ times.
\
Compare the mean bootstrap bias and bootstrap standard error with the theoretical ones. Comment on the results.

## Answer
```{r}
set.seed(1234)
n <- c(5,10,20)
B <- 1000
m <- 1000
j<-1
#模拟一千次
while(j<=m){
for(i in 1:length(n)){
  x <- rexp(n[i],2)
  lambda<-mean(x)
  lambdastar <- numeric(B)
  for(b in 1:B)
  {
   xstar<-sample(x,replace=TRUE)
   lambdastar[b]<-mean(xstar)
  }
y<-c(bias=mean(lambdastar)-lambda,se.boot=sd(lambdastar),se.samp=sd(x)/sqrt(length(x)))
j<-j+1
}
}
```

理论上的mean bootstrap bias 是$\lambda /(n-1)$. The standard error $\hat{\lambda}$ is $\lambda n /[(n-1) \sqrt{n-2}]$
```{r}
set.seed(1234)
n <- c(5,10,20)
bias<-numeric(3)
standarderror<-numeric(3)
lambda<-2
for (i in 1:length(n)){
  bias[i]<- 2/(n[i]-1)
  standarderror[i]<- 2*n[i]/((n[i]-1)*sqrt(n[i]-2))
}
bias
standarderror
```
由结果可知，模拟的结果与理论计算的结果大致相同，说明boostrap方法模拟出的结果值效果较好与理论相近。

## Question
Obtain a bootstrap t confidence interval estimate for the correlation statistic in Example 7.2 (law data in bootstrap).

## Answer
Bootstrap的t置信区间的表达式如下：
$$\left(\hat{\theta}-t_{1-\alpha / 2}^* \widehat{s e}(\hat{\theta}), \quad \hat{\theta}-t_{\alpha / 2}^* \widehat{s e}(\hat{\theta})\right)$$
Bootstrap的t置信区间计算步骤如下：
\
1. Compute the observed statistic $\hat{\theta}$.
\
2. For each replicate, indexed $b=1, \ldots, B$ :
(a) Sample with replacement from $x$ to get the $b^{\text {th }}$ sample $x^{(b)}=\left(x_1^{(b)}, \ldots, x_n^{(b)}\right)$.
(b) Compute $\hat{\theta}^{(b)}$ from the $b^{\text {th }}$ sample $x^{(b)}$.
(c) Compute or estimate the standard error $\widehat{s e}\left(\hat{\theta}^{(b)}\right)$ (a separate estimate for each bootstrap sample; a bootstrap estimate will resample from the current bootstrap sample $x^{(b)}$, not $x$ ).
(d) Compute the $b^{t h}$ replicate of the "t" statistic, $t^{(b)}=\frac{\hat{\theta}^{(b)}-\hat{\theta}}{\widehat{s e}\left(\hat{\theta}^{(b)}\right)}$.
\
3. The sample of replicates $t^{(1)}, \ldots, t^{(B)}$ is the reference distribution for bootstrap $t$. Find the sample quantiles $t_{\alpha / 2}^*$ and $t_{1-\alpha / 2}^*$ from the ordered sample of replicates $t^{(b)}$.
\
4. Compute $\widehat{s e}(\hat{\theta})$, the sample standard deviation of the replicates $\hat{\theta}^{(b)}$.
\
5. Compute confidence limits
$$
\left(\hat{\theta}-t_{1-\alpha / 2}^* \widehat{s e}(\hat{\theta}), \quad \hat{\theta}-t_{\alpha / 2}^* \widehat{s e}(\hat{\theta})\right)
$$
\
首先，编写函数用于计算样本的bootstrap t置信区间。
```{r}
BOOT.t.ci <- function(x, B = 500, R = 100, level = .95, statistic){
#计算 bootstrap的t置信区间
x <- as.matrix(x)
n <- nrow(x)
se <- numeric(B)
STAT <- numeric(B)
#用局部函数去计算bootstrap
BOOT.se <- function(x, R, f) {
m <- nrow(x)
x <- as.matrix(x)
TH <- replicate(R, expr = {
  i <- sample(1:m, size = m, replace = TRUE)
  f(x[i, ])
})
return(sd(TH))
}
for (b in 1:B) {
j <- sample(1:n, size = n, replace = TRUE)
y <- x[j, ]
STAT[b] <- statistic(y)
stat1 <- statistic(x)
se[b] <- BOOT.se(y, R = R, f = statistic)
}
T.stats <- (STAT - stat1) / se
Alpha <- 1 - level
SE0 <- sd(STAT)
QT <- quantile(T.stats, c(Alpha/2, 1-Alpha/2), type = 1)
names(QT) <- rev(names(QT))
CI <- rev(stat1 - QT * SE0)
}
```
将函数运用到Eample7.2中求出相关系数对应的t置信区间。
```{r}
LSAT<-c(576,635,558,578,666,580,555,661,651,605,653,575,545,572,594)
GPA<-c(339,330,281,303,344,307,300,343,336,313,312,274,276,288,296)
data <- cbind(LSAT, GPA)
stat <- function(data) {
cor(data[,1],data[,2])}
CI <- BOOT.t.ci(data, statistic = stat, B=2000, R=200)
print(CI)
```
