---
title: "SISISIS"
author: "Jingqi Ding"
date: "2023-11-27"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to R-package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Introduction
This r package is in response to an article by scholar Fan Jianqing in the Journal of the Royal Statistical Society in 2008 called Sure independence screening for ultrahigh The dimensional feature space r package is a simulation based on the fourth part of the paper, which explores the accuracy estimation of the model by SIS, lasso, and ISIS. The accuracy of the estimation by SIS and ISIS methods is given here. This is the estimated accuracy of the two methods.
```{r}
SIS <- function(x,y,d,xtrue){
  SIS_flag <- 0
  n=nrow(x)
  p=ncol(x)
  R=c(rep(0,p))
  for(i in 1:p){
    R[i]=(sum(((y-mean(y))*x[,i]))/sd(x[,i]))^2
  }
  r=order(R,decreasing=T)
  if(all( xtrue %in% r[1:d]))
    SIS_flag <- 1
  return(list(select=r[1:d],SIS_flag=SIS_flag))
}

SIS.SCAD <- function(x,y,d,xtrue){
  p <- ncol(x)
  beta_SIS.SCAD <- c(rep(0,p))
  m <- SIS(x,y,d,c(1,2,3))$select
  fit_scad <- cv.ncvreg(x[,m],y,penalty="SCAD")
  beta_SIS.SCAD[m]<-as.vector(coef(fit_scad))[2:(d+1)]
  A <- which(abs(beta_SIS.SCAD)>0)
  size <- length(A)
  return(list(A=A,size=size))
}

ISIS <- function(x,y,d,xtrue){
  size <- 0
  ISIS_flag <- 0
  AA <- c()
  yy=y
  xx=x
  while(size<d)
  {
    B <- SIS.SCAD(x,y,d,xtrue)
    m <- B$size
    if(m>0){
      ISIS_data <- data.frame(y,x[,B$A])
      model <-lm(y~x[,B$A],data = ISIS_data)
      AA <- c(B$A,AA)
      size <- size + m
      x <- x[,-B$A]
      residual <- residuals(model)
      y <- residual
    }
    else break
  }
  x=xx
  y=yy
  if(all( xtrue %in% AA))
    ISIS_flag <- 1
  return(list(ISIS_flag=ISIS_flag,AA=AA))
}
```

## Introduction
We construct an ordinary linear model, which is a high-dimensional variable screening problem. We use the constructed function to determine whether the function can accurately select variables for the model we generate.
```{r}
set.seed(1234)
library(MASS)
library(glmnet)
library(ncvreg)
SIS_flag1  <- 0
ISIS_flag1  <- 0
SIS_result1 <- 0
ISIS_result1 <- 0
p <- 100
n <- 20
rho <- 0.1
k <- 50
xtrue<-c(1,2,3)
d <- 2.5*floor(n/log(n))
for(i in 1:k){
  beta <- c(5,5,5,rep(0,(p-3)))
  mean <- c(rep(0,p))
  sigma <- matrix(c(rep(0.5,p*p)), nrow=p, ncol=p)+diag(p)*(1-rho)
  x <- mvrnorm(n, mean, sigma)
  y <- x%*%beta+rnorm(n)
  #SIS
  SIS_flag1 <- SIS_flag1+SIS(x,y,d,c(1,2,3))$SIS_flag
  #ISIS
  ISIS_flag1 <- ISIS_flag1+ISIS(x,y,d,c(1,2,3))$ISIS_flag
}
SIS_result1 <- SIS_flag1/k
ISIS_result1 <- ISIS_flag1/k

SIS_result1
ISIS_result1
```

