---
title: "Homework-2023.09.18"
author: "丁婧琦"
date: "2023-9-18"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to R-package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Question
\
**3.2:The standard Laplace distribution has density $f(x) = 12*\exp−|x|, x\in R$. Use the inverse transform method to generate a random sample of size 1000 from this distribution. Use one of the methods shown in this chapter to compare the generated sample to the target distribution.**
\
## Answer 
\
1. Derive the inverse function $F_x^{-1}(u)$.
\
2. Write a command or function to compute $F_x^{-1}(u)$.
\
3. For each random variate required:
\
(a) Generate a random u from Uniform(0,1).
(b) Deliver x = $F_x^{-1}(u)$
```{r}
#使用逆变换方法从该分布生成大小为1000的随机样本
n <- 1000
u <-runif(n)
x <- abs(log(12/u))
x
#样本与目标分布进行比较
hist(x, prob = TRUE, main = expression(f(x)==12*exp(-abs(x))), xlab = "value")
y<-seq(0,10,0.01)
lines(y,12*exp(-abs(y)))
```
\
## Question
\
**3.7:Write a function to generate a random sample of size n from the Beta(a,b)distribution by the acceptance-rejection method. Generate a random sample of size 1000 from the Beta(3,2) distribution. Graph the histogram of the sample with the theoretical Beta(3,2) density superimposed.**
\
## Answer
\
采用Acceptance-rejection 的算法：令g(x) = 1, 0 < x < 1 和 $c=\frac 1{B(a,b)}$.
```{r}
#编写函数
Myfunction <- function(m,n){
  N <- 1000
  j <- 0
  i <- 0
  y <- numeric(N)
  while (i < N)
  {u <- runif(1)
  j <- j + 1
  x <- runif(1)
  if (x^(m-1) * (1-x)^(n-1)> u)
  #选择上界c为1/B(a,b)，g(x)为U(0,1)均匀分布的密度函数
  {
    i <- i + 1
    y[i] <- x
  }
  j
  }
  return(y)
}
Myfunction(3,2)
#用理论Beta(3,2)密度叠加的样本直方图。
hist(Myfunction(3,2), freq = FALSE, breaks = seq(0,1,0.01), main = "histogram of the sample with the theoretical Beta(3,2) density", xlab = "value")
ff <- function(x) {
  x^2*(1-x)^{2-1}/beta(3,2)}
curve(ff, 0, 1,col = 2, add = TRUE)   
legend('topleft',"real density", col = 2, lwd = 1, cex=0.7)
```
##Question
\
3.9:The rescaled Epane chnikov kernel is a symmetric density function$$f_e(x)=\frac 34*(1-x^2),\quad |x|\le 1$$ 
Devroye and Gy¨orfi give the following algorithm for simulation from this distribution. Generate iid U1, U2, U3 ∼ Uniform(−1, 1). If $|U3| \ge|U2|$ and $|U3|\ge|U1|$, deliver U2; otherwise deliver U3. Write a function to generate random variates from $f_e$, and construct the histogram density estimate of a large simulated random sample.
\

## Answer
```{r}
UU1 <- runif(10000, min = -1, max = 1)    
UU2 <- runif(10000, min = -1, max = 1)
UU3 <- runif(10000, min = -1, max = 1)
UU <- ifelse((abs(UU3)>abs(UU2) & abs(UU3)>abs(UU1)), UU2, UU3)
hist(UU, freq = FALSE, breaks = seq(-1,1,0.01), main = "histogram density estimate of a large simulated random sample", xlab = "value")
ff <- function(X) {3/4*(1-X^2)}
curve(ff, -1, 1, col = 2, add = TRUE)   
legend('topleft',"real density", col = 2, lwd = 1, cex=0.6)   

```
\
## Question
\
**3.10:Prove that the algorithm given in Exercise 3.9 generates variates from the density $f_e$ (3.10).**
\
## Answer
\
不妨设 $X_1=|U1|, X_2=|U2|, X_3=|U3|$,由$X_1,X_2,X_3$的定义易得： $X_1,X_2,X_3 \sim$ U(0,1)。 

令 $X= \begin{cases}
X_2 \quad X_3 \ge X_1和X_3 \ge X_2 \\
X_3 \quad 其他 \\
\end{cases}$  
由于$f_a(x)$是对称的, 我们需要证明$X$ 服从以下分布：  
$$f_{a'}(x)=2*\frac 34(1-x^2),\quad 0 \le x \le 1$$  

生成 $X$的算法如下 :  
\
1. 生成 $X_1,X_2,X_3 \sim$ U(0,1)。
2. 去除三个变量中最大的 $X_{(3)}$ 。
3. 从剩下的两个变量中选择一个具有相同概率的变量，并令$X$为这个变量的值。  

对于任意满足 $0 \le x \le 1$的$x$,可以构造下面这两个集合:  
A={只有一个 $X_i \le x$ }  
B={至少两个 $X_i \le x$ },  
通过这两个集合可以计算出$X$的分布函数, 因此可以得出$F_{a'}(x)$ 的计算表达式为:

\begin{align*}
F_{a'}(x)&=P(X\le x)\\
&=P(X \le x,A)+P(X \le x,B)\\
&=P(X \le x~|~A)*P(A) + P(X \le x~|~B)*P(B)\\
&=\frac 12*3x(1-x)^2 + 1*[3x^2(1-x) + x^3]\\
&=-\frac 12 x^3 +\frac 32 x,\quad 0 \le x \le 1
\end{align*}  

因此，$X$ 的密度函数为：
$$ f_{a'}(x)=F'_{a'}(x)=2*\frac 34(1-x^2),\quad 0 \le x \le 1 $$  
可以说明该算法对应产生的密度函数是$f_a$ 。
\
##Question
\
**课后习题：利用逆变化复现函数sample的部分功能（replace=TURE)**
\
##Answer
\
sample函数对应的参数形式如下：sample(x,size,replace,prob)
\
其中，x为一个可供选择的一个或多个元素的向量，或一个整数。size为一个非负数，是指的可控选择的项目数。replace代表是否发生替换，True相当于无放回抽样，False相当于有放回抽样。prob代表被采样元素的概率权重向量。
```{r}
#首先考虑默认情况，相当于随机的有放回抽样。要抽取的数组a所对应的编号相当于离散型的随机变量x，生成的均匀分布的随机数为y。因此可以用逆变换来生成对应的随机数编号。
my.sample1 <- function(a,b){
c <-length(a)
   x <- seq(1, c, 1)#数组a产生的编号
   p <- rep(1:1,c)/c#每个编号所对应的概率
   cp <- c(0,cumsum(p)) #累加得到分布函数
   y1 = numeric(b)
  for(j in 1:b)#一共进行b次，抽取b个数据
  { u=runif(1)#产生随机数
    for(i in 1:(length(cp)-1))
     { if(u>cp[i] & u<=cp[i+1])#利用逆变换的到x（即对应的编号）
        {y1[j]=x[i]
          break}
    }
   }
  return(a[y1])
}
#举例
a<-c(1,4,5,2,7,9,6,46,0,8)
my.sample1(a,3)
my.sample1(a,2)
#考虑，replace等于TRUE的情况，相当于随机的无放回抽样。
my.sample2 <- function(a,b){
  c <-length(a)
  x <- seq(1, c, 1)#数组a产生的编号
  p <- rep(1:1,c)/c#每个编号所对应的概率
  cp <- c(0,cumsum(p)) #累加得到分布函数
  y1 = numeric(b)
  j=1
  while(j<=b)#一共进行b次，抽取b个数据
  { u=runif(1)#产生随机数
    for(i in 1:(length(cp)-1))
    if(u>cp[i] & u<=cp[i+1])#利用逆变换的到x（即对应的编号）
    {xx=x[i]
      break
    }
    m=1
    flag=1#用于标记是否符合不重复的条件
    while(m<=j){
     if(y1[m]==xx)#判断是否与之前的有重复
      { flag=0
      break
      }
    m=m+1
    }
    if(flag==1)#不与之前的重复，则放入y1中
    { y1[j]=xx
       j=j+1
    }
  }
 return(a[y1])
}

#举例
b<-c(32,34,1,5,65,74,89)
my.sample2(b,4)
my.sample2(b,2)
```
