---
title: "Homework-10.30"
author: "丁婧琦"
date: "2023-10-30"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to R-package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Question
Implement the two-sample Cramér-von Mises test for equal distributions as a permutation test. Apply the test to the data in Examples 8.1 and 8.2.

## Answer
Two-sample tests for univariate data：Cramer-von Mises statistic.The Cramér-von Mises statistic, which estimates the integrated
squared distance between the distributions, is defined by
$$W_2=\frac{m n}{(m+n)^2}\left[\sum_{i=1}^n\left(F_n\left(x_i\right)-G_m\left(x_i\right)\right)^2+\sum_{j=1}^m\left(F_n\left(y_j\right)-G_m\left(y_j\right)\right)^2\right]$$
Fn: the ecdf of the sample x1, . . . , xn; Gm: the ecdf of the sample y1, . . . , ym.
\
Apply the test to the data in Examples 8.1 and 8.2.
```{r}
attach(chickwts)
x <- sort(as.vector(weight[feed == "soybean"]))
y <- sort(as.vector(weight[feed == "linseed"]))
detach(chickwts)
cat(x,'\n')
cat(y,'\n')

n<-length(x)
m<-length(y)
cvmtest <- function(x,y){
#样本x1到xn的ecdf
fn<-function(a){
  flag1<-0
  for(i in 1:length(x)){
    if(x[i]<=a)
      flag1 <- flag1+1
  }
  return(flag1/length(x))
}
#样本y1到ym的ecdf
gm<-function(b){
  flag2<-0
  for(j in 1:length(y)){
    if(y[j]<=b)
      flag2 <- flag2+1
  }
  return(flag2/length(y))
}
#统计量W2
sum1<-sum2<-0
for(i in 1:n){
  sum1<-sum1+(fn(x[i])-gm(x[i]))^2
}
for(j in 1:m){
  sum2<-sum2+(fn(y[j])-gm(y[j]))^2
}
W2<-(sum1+sum2)*m*n/(m+n)^2  
return(W2)
}

R <- 999 #number of replicates
z <- c(x, y) #pooled sample
K <- 1:26
W2 <- numeric(R) #storage for replicates
W20 <- cvmtest(x,y)
for (i in 1:R) {
#generate indices k for the first sample
k <- sample(K, size = 14, replace = FALSE)
x1 <- z[k]
y1 <- z[-k] #complement of x1
W2[i] <- cvmtest(x1,y1)
}
p <- mean(c(W20, W2) >= W20)
p
```

## Question

The Count 5 test for equal variances in Section 6.4 is based on the maximum number of extreme points. Example 6.15 shows that the Count 5 criterion is not applicable for unequal sample sizes. Implement a permutation test for equal variance based on the maximum number of extreme points that applies when sample sizes are not necessarily equal.

## Answer
McGrath和Yeh引入的两样本“Count Five”方差相等检验计算每个样本相对于另一个样本的极值点的数量。假设两个样本的均值相等，样本容量相等。如果一个样本中的观察结果不在另一个样本的范围内，则认为是极端的。如果任一样本有五个或五个以上的极值点，则拒绝等方差假设。

```{r}
set.seed(1234)
# Count 5 test
COUNT5test = function(x, y) {
X = x - mean(x)
Y = y - mean(y)
OUTx = sum(X > max(Y)) + sum(X < min(Y))#统计极值点
OUTy = sum(Y > max(X)) + sum(Y < min(X))
return(as.integer(max(c(OUTx, OUTy)) > 5))# 返回1 则拒绝等方差的原假设，返回0则不能拒绝等方差的假设
}
```

根据Count 5 test写出Count 5 test permutation
```{r}
# Count 5 test permutation
COUNT5test_permutation = function(a) {
n = length(a)
x = a[1:(n/2)]
y = a[-(1:(n/2))]
X = x - mean(x)
Y = y - mean(y)
OUTx = sum(X > max(Y)) + sum(X < min(Y)) 
OUTy = sum(Y > max(X)) + sum(Y < min(X))# 返回1 则拒绝等方差的原假设，返回0则不能拒绝等方差的假设
return(as.integer(max(c(OUTx, OUTy)) > 5))
}

permutation = function(a,R) {
  n = length(a)
  result = numeric(R)
  for (r in 1: R){
      i = sample(1:n ,n ,replace = FALSE)
      result[r] = COUNT5test_permutation(z[i])
  }
  sum(result)/R
}              
```

Example 6.15 shows that the Count 5 criterion is not applicable for unequal sample sizes.We are estimating the empirical Type I error
rate when sample sizes differ and the “Count Five Permutation” test criterion is applied. Each sample is centered by subtracting the sample mean.
```{r}
n1 <- 20
n2 <- 50
mu1 <- mu2 <- 0
sigma1 <- sigma2 <- 1
m = 10000

Alphahat1 = mean(replicate(m, expr={
x = rnorm(n1, mu1, sigma1)
y = rnorm(n2, mu2, sigma2)
x = x - mean(x) #centered by sample mean
y = y - mean(y)
COUNT5test(x, y)
}))

Alphahat2 = mean(replicate(m, expr={
x = rnorm(n1, mu1, sigma1)
y = rnorm(n2, mu2, sigma2)
x = x - mean(x) #centered by sample mean 
y = y - mean(y)
z = c(x,y)
permutation(z,1000) 
})<0.05)

round(c(COUNT5test=Alphahat1,COUNT5test_permutation=Alphahat2),5)
```
由结果可知，Count 5 test 的显著性水平远高于Count 5 permutation的显著性水平。

## Question
Proof the Stationarity of Metropolis-Hastings sampler Algorithm in continuous situation.

## Answer
在连续的情况下，Metropolis-Hastings Algorithm的具体式子如下：
\
1.Target pdf: f(x)
\
2.proposal distribution:g(r|s)
\
3.acceptance probability:$\alpha(s,r)=min({\frac {f(r)g(s|r)}{f(s)g(r|s)},1})$
\
4.transition kernel:$K(s,r)=\alpha(r,s)g(s|r)+I(s=r)[1-\int\alpha(r,s)g(s|r)ds]$
\
5.stationarity:$K(s,r)f(s)=K(r,s)f(r)$
\
（一）当r=s时，显然有$K(s,r)f(s)=K(r,s)f(r)$
\
（二）当r≠s时，
$$K(s,r)f(s)=\alpha(s,r)g(r|s)f(s)=min({\frac {f(r)g(s|r)}{f(s)g(r|s)},1})g(r|s)f(s)$$
则$K(s,r)f(s)$的值为:
\left\{\begin{matrix}
  & g(s|r)f(s)\quad f(s)g(r|s)\leq f(r)g(s|r)\\
  &f(r)g(s|r)\quad  f(r)g(s|r)\leq f(s)g(r|s)
\end{matrix}\right.
\

$$K(r,s)f(r)=\alpha(r,s)g(s|r)f(r)=min({\frac {f(s)g(r|s)}{f(r)g(s|r)},1})g(s|r)f(r)$$
则$K(r,s)f(r)$的值为:
\left\{\begin{matrix}
  & g(s|r)f(s)\quad f(s)g(r|s)\leq f(r)g(s|r)\\
  &f(r)g(s|r)\quad  f(r)g(s|r)\leq f(s)g(r|s)
\end{matrix}\right.
因此，可得$K(r,s)f(r)=K(s,r)f(s)$,这说明连续情况下Metropolis-Hastings sampler 算法仍然具有平稳性。
